The mass distribution of companions to low-mass white dwarfs

### 2014-11-11 documents/letter/response.txt

Dear Dr. de Grijs

We thank the two referees for their detailed comments. We have improved the paper, and included all the suggestions in the revised manuscript. Our response to the referees’ suggestions are below.

Please let me know if further improvements are required.

Sincerely,
Jeff J Andrews

>
>========================================================
>Report from Referee 1:
>
>The authors investigate the mass distribution of companions to
>low-mass white dwarfs. For this purpose they have developed a
>thorough statistical model, which has been applied to three mock data
>sets as well as to the real ELM white dwarf sample. They find that the
>companion mass distribution of the EML sample peaks at 0.71Msun (std
>of 0.26Msun), and that the NS fraction seems to be very low.
>
>The paper is well-written, goes to the point, and is well
>understood. Thus I highly recommend its publication in ApJ
>letters. However, before this I consider there are some points the
>authors should discuss/investigate further. 
>
>- Title. Since the sample of study is the ELM sample (defined as
>Mwd<~0.3Msun), instead of the low-mass sample (defined as
>Mwd<~0.45Msun), change the title to "The mass distribution of
>companions to extremely low-mass white dwarfs".
>
>- Abstract. "We then apply this model to a sample of low mass white
>dwarfs (LMWDs, M<~0.45 Msun)." Reading this gives the impression that
>the sample is an observed (real) one, which is not the case. Specify
>that the low-mass WD samples used are three, and that these are drawn
>from mock data.
>

We have fixed this in the abstract.

>
>- Introduction. The authors cite the seminal paper by Marsh et
>al. (1995) that demonstrated that a large fraction of low-mass white
>dwarfs are in binaries. However, several more and recent observational
>efforts have been performed that prove to high extent that indeed
>low-mass white dwarfs are formed due to binary interactions. Add 
>citations to e.g. Maxted et al. 2000MNRAS,319,305M, Rebassa-Mansergas 
>et al. 2011MNRAS,413,1121R.
>

These citations have been added to the introduction, along with a result from the SPY survey, searching for SN Ia progenitors, which identified two additional LMWDs in close binaries with unknown companions.

>
>- Introduction. The authors should state more clearly why identifying
>NS or WD companions to ELM white dwarfs is important. What important
>problems will be solved or can be addressed by knowing that NS are or
>are not likely to be the companions of ELM white dwarfs?
>

We have added a sentence explaining the importance of finding individual NS-LMWD systems in paragraph 2 in the introduction and a sentence explaining the importance of understanding the companion mass distribution to LMWDs in paragraph 4.

>
>- Section 2. Why using a logarithmic prior for sigma(WD)?

We choose a logarithmic prior for sigma(WD) since it is scale invariant. We have added this to the text.

>Why fixing sigma(NS) to 0.05Msun when sigma(WD) has a much wider range? Is it because the NS mass distribution peaks at ~1.35Msun with almost no tail towards lower and higher masses?

We wanted to build a simplistic model, with few parameters, therefore we set the NS distribution without allowing it to vary. From Kiziltan et al. (2013) and Smedley et al. (2014) it appears that NSs with WD companions may have a slightly higher mass tail, therefore we set the NS mass distribution higher than the canonical value of 1.35 Msun.

>According to the text, sigma(WD) ranges from 0.02-2Msun. However, in Table 1 I see sigma(WD) proportional to sigma^(-1), where 0.02 
>- Table 1. The prior of mu(WD) is written as U(0.2,1), but should not it be U(0.2,1.4)?

The prior on sigma(WD) should be U(0.2,2.0) and on mu(WD), 0.02 < mu < 1.0. Both the text and table have been fixed to reflect this. For the flexibility of our model, we allow sigma(WD) to vary greatly. We still truncate the mass distribution at [0.2,1.44], but we do not allow the center of the Gaussian to go above 1.0 Msun.

>
>- Figure 1. Why not adding the number and label in the y axis? Top
>left panel. It is interesting to see that the distribution is
>bi-modal, and that there is a large number of massive (~1Msun) white
>dwarfs. How realistic are the assumptions for this particular M2
>distribution?
>

The distribution in Figure 1 was drawn from a Gaussian with mu(WD)=0.7 Msun and sigma(WD) = 0.2. We tested this by drawing other random samples; the bimodal distribution is due to the randomness of drawing 100 WD samples. In other randomly drawn samples, this distribution appears as a single Gaussian.

>
>- I consider testing the statistical model using three samples of mock
>data is very useful. However, I believe the model should also be
>tested with real data. The sample of close white dwarf-M dwarf
>binaries with orbital periods and component masses measured is of the
>same order as the ELM survey and can be used for this purpose (see
>e.g. Nebot Gomez-Moran et al. 2011A&A,536A,43N; there are also several
>known eclipsing systems: see the work by S.G. Parsons et al.). In this
>case, K are known for the secondary stars so the distribution to test
>with the statistical model would be the white dwarf mass
>distribution. (Note that for this sample the spectral type of the
>secondary stars are provided, which can be converted into mass
>following a spectral type-mass relation: e.g. Baraffe & Chabrier
>1996ApJ,461L,51B).
>

Based on your suggestion, we have added a fourth test where we derive the resulting WD mass distribution of companions to the post-common envelope binary sample from SDSS. The description of this test is included in Section 3.4, and the results are included in Figure 4.

>
>- Section 4.1. "Fitting the WDs' spectra to templates provides
>precisely determined M1 values". I am not entirely convinced by this
>sentence. This is definitely the case when one of the stars is
>considerably more luminous than the other, but it might not be the
>case otherwise. Lets consider a white dwarf which contributes 30% to
>the total flux in the Hbeta to Hepsilon Balmer line regime (where the
>line profile fitting takes place), the other white dwarf contributing
>70%. The total flux will be the sum of the two flux contributions and
>a fit to the resulting spectrum may not give the mass of the more
>luminous white dwarf. I agree that assuming M1 to be the one obtained
>from the template fit is the best way to proceed, however a note of
>caution should be added in the text. A plausible way to check this
>would be to compare the accurate masses of the eclipsing systems with
>those provided from the spectral fitting, if available.
>

There is a distinct possibility that the companion WDs could contribute to the luminosity of the LMWD primaries in these systems. However, Gianninas et al. (2014) point out that because the systems are all single-lined spectra, they expect the companion’s “contribution to the observed spectra to be on the order of a few percent at most.” In investigating this possibility though, we found a bigger issue: For two of the three eclipsing systems, the spectroscopic mass measurements are in agreement with the expectation from the eclipse measurement. For the third system, NLTT 11748, there is a significant discrepancy. Gianninas et al. (2014) contribute this difference to the “high log g problem”, a manifestation of the problems with using 1-D WD atmospheric models. They suggest that only the spectroscopic masses of the seven WDs with temperatures below roughly 9500 K will be affected. We add a note of caution in the text to indicate there may be some unknown uncertainties in these mass measurements.

>
>- Section 4.2. "Our distribution is significantly wider (sigma ~ 0.26
>Msun compared with sigma~0.1 Msun), possibly due to mass transfer
>affecting the mass distribution of the unseen primary WDs as well." Do
>the authors mean on-going mass transfer? If that is the case, should
>we not see an accretion disk in the spectrum? It seems unlikely that a
>large fraction of these systems are currently undergoing mass transfer
>episodes. Or do the authors mean previous mass transfer episodes? When
>specifically?
>

We expect that all these systems are detached due to the lack of emission lines in the spectra as would be expected from an accretion disk. The text has been updated to specify that the companion masses may be more massive due to previous mass transfer phases.

>
>- Section 4.2. Since the ELM sample contains primaries of M<~0.3Msun
>and mu(WD)=0.71Msun, this seems to imply that the future mergers will
>not produce type Ia supernovae. I consider the authors should add a
>couple of sentences discussing this.
>

While most of these systems almost certainly have a combined mass less than 1.4 Msun, many of the combined masses of these systems are still ~1Msun. They may therefore evolve into underluminous supernova. We have included some discussion of this in Section 4.2.

>
>- Inspection of figure 3 and the right panel of figure 4 reveals that
>P(NS) increases with mf. Add an explanation why this is the case. Do
>these figures imply that an observer looking for a NS in orbit with a
>ELM white dwarf can focus specifically on targets with the highest mf?
>If so, add a sentence stating this in the text.
>

Systems with higher mf values are more likely to have NS companions through Equation 1. We added a note about this in the text.

>****
>Report from Referee 2:
>
>I provide here comments only on the statistical methodology of this manuscript, not on any scientific aspects. I have not checked the equations (8)-(15) in detail. 
>
>The procedure in section 2 focuses on the question raised in the Introduction: "1. Can the population as a whole be modeled using a simple description of the companion masses?" The setup of the likelihood seems reasonable. The normal mixture model for white dwarf and neutron star secondaries is also reasonable. The inference that the secondary WDs have similar mass distributions as primary WDs is unsurprising and adds confidence that the calculation is reasonable. I have two comments:
>
>A. Bayes' rule is only needed if significant priors are introduced. Are equations (7) and (19)-(20) relevant prior distributions? If so, please label them accordingly. Indeed, the authors state in 4.2/par2 that the "results are independent of astrophysical expectations as they do not include informative priors on ..."; but the entire point of the Bayesian approach is to introduce meaningful priors. Since the authors seek the MAP solution, I suspect the calculation is equivalent to a constrained maximum likelihood calculation (e.g. http://link.springer.com/article/10.1023/A:1008669208700 http://faculty.washington.edu/rons/cmlinf/cmlinf.html). There is no difficulty in using an MCMC approach, and the results are unchanged, but the authors should clarify that the calculation can be viewed from either perspective. Fortunately the authors do not emphasize `Bayesian' in the title, abstract or conclusions. 
>

The prior in equation 7 comes from the fact that the inclination angle is random. One of the advantages to this sample is that there is (nearly) no observational bias on the inclination angle, therefore this prior is appropriate. The priors on our NS model, listed in Equations 19-20, are reasonable based on NS mass measurements derived elsewhere, in Kiziltan et al. (2013) and Smedley et al. (2014).

We agree that there is no difference between our method and a maximum likelihood calculation. We have added a sentence clarifying this in the first paragraph of Section 2.

>
>B. Concerning the statement in 4.2 "Our distribution is significantly wider ....[physical explanation]. Couldn't this be a statistical effect: Wouldn't the posterior distribution appear wider just because the sample is small and the spread is thus poorly constrained? This can be checked with simulations of different sample sizes.
>
>

### 2014-11-11 documents/letter/ms.tex
Updated .tex and .bib and added referee response

\begin{abstract}
Measuring the masses of companions to single-line spectroscopic binary stars is (in general) not possible because of the unknown orbital plane inclination.  Even when the mass of the visible star can be measured, only a lower limit can be placed on the mass of the unseen companion. However, since these inclination angles should be isotropically distributed, for a large enough, unbiased sample, the  companion mass distribution can be deconvolved from the distribution of observables. In this work, we construct a hierarchical probabilistic model to infer properties of unseen companion stars given observations of the orbital period and projected radial velocity of the primary star. We then apply this model to a sample of low mass white dwarfs (LMWDs, $M\lesssim0.45~\Msun$). We use a mixture of two Gaussians to model the WD and neutron star (NS) companion mass distributions. Our model successfully recovers the initial parameters of several mock data sets. We then apply our model to 55 WDs in the extremely low mass (ELM) WD Survey. Our maximum a posteriori model for the WD companion population has a mean mass, $\mu_{\rm WD}$, of $0.71~\Msun$ with a standard deviation, $\sigma_{\rm WD}$, of $0.26~\Msun$; the fraction of NS companions, $f_{\rm NS}$, is consistent with zero. However, the marginal posterior distribution over the NS fraction has a significant tail up to $f_{\rm NS} \approx 16\%$. We make samples from the posterior distribution publicly available so that future observational efforts may compute the NS probability for newly discovered low mass WDs.
\end{abstract}

@@

Except in cases of extreme metallicity \citep{kilic07}, the Galaxy is not old enough to produce LMWDs ($M\lesssim0.45~ \Msun$) through single star evolution. These objects are formed through dynamical interactions with another star, and are therefore expected to be found in binary systems \citep{han98,nelemans00,nelemans01,vdSluys06,woods12}. In their seminal work, \citet{marsh95} discovered companions to five LMWDs, confirming these theoretical expectations. The ELM WD Survey \citep{ELMI} identifies LMWDs in the Sloan Digital Sky Survey \citep[SDSS;][]{york00} and elsewhere for spectroscopic follow-up, focusing on extremely low mass WDs ($M\lesssim0.3~ \Msun$). After these authors' initial investigation found that 11 of 12 LMWDs had close binary companions, further spectroscopic follow-up has now brought the sample of ELM WDs to 61 systems, 55 of which have measured radial velocity amplitudes and orbital periods \citep{ELMII, ELMIII, ELMIV, ELMV}. We refer to these 55 systems as the ELM sample.

While the orbital periods and radial velocities indicate the companions to these LMWDs are most likely WDs, due to the unmeasured inclination angle, LMWDs could host NS companions \citep{vLeeuwen07}. Indeed, LMWDs are observed as companions of millisecond pulsars \citep{vKerkwijk96,callanan98,bassa06,antoniadis12}. However, radio searches for pulsed emission and searches for X-ray emission from LMWD companions have been unsuccessful \citep{agueros09b,agueros09a,kilic13}.

@@

The ELM sample is now large enough that the companion mass distribution, and importantly the NS fraction, can be statistically constrained. In this work, we develop a probabilistic model to infer parameters of an assumed form for the mass distribution of companions to LMWDs. Our method is similar to that employed by \citet{ozel12} and \citet{kiziltan13} to describe the mass distribution of NSs in binaries using post-Keplerian parameters. We focus on several specific questions: 1.\ Can the population as a whole be modeled using a simple description of the companion masses? 2.\ How does the companion mass distribution compare to predictions from population synthesis simulations?  3.\ What is the rate of NS-LMWD binaries implied by our model? 4.\ What are the resulting distributions of NS probabilities for individual systems in the ELM sample?

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[angle=90,width=0.95\columnwidth]{Porb_M1.eps}
\caption{The $M_1$ - $\period$ distribution of the ELM WD sample (circles) and the known WD-NS binaries (triangles). The three eclipsing systems in the ELM sample with known $M_2$ are shown as filled circles, and the masses of the ELM WDs without detected radial velocity variations are shown by the arrows. From $M_1$ and $\period$ alone, the two populations are indistinguishable.}
\label{fig:Porb-M1}
\end{center}
\end{figure}

@@

We must now choose a functional form for the companion mass distribution,  $p(M_2\given \bs{\theta})$. For all experiments -- including that with the real data -- we use a two-component Gaussian mixture model to fit the data. We generate mock data with different mixture component forms. We truncate the distributions using physically motivated bounds so that the WD component is restricted to the range $M_2\in [0.2,\wdupper]~\Msun$ and the NS component is restricted to $M_2\in [1.3,2.0]~\Msun$. We then have:
\begin{align}
	p(M_2 \given \bs{\theta}) &= \left[ (1-f_{\rm NS})~p_{\rm WD} + f_{\rm NS}~p_{\rm NS} \right] 
\end{align}
where 
\begin{align}
	p_{\rm WD} &= \mathcal{N}(M_2 \given \mu_{\rm WD}, \sigma^2_{\rm WD}); ~0.2 < \frac{M_2}{\Msun} < \wdupper, \\
	p_{\rm NS} &= \mathcal{N}(M_2 \given \mu_{\rm NS}, \sigma^2_{\rm NS}); ~1.3 < \frac{M_2}{\Msun} < 2,
\end{align}
and $\mathcal{N}$ is the (truncated, but properly normalized) normal distribution with mean $\mu$ and variance $\sigma^2$, and the distributions are limited to the ranges specified. We fix $\mu_{\rm NS}$ and $\sigma_{\rm NS}$ to:
\begin{align}
	\mu_{\rm NS} &= 1.4~\Msun\\
	\sigma_{\rm NS} &= 0.05~\Msun
\end{align}
based on indications that NSs in certain binaries may be somewhat more massive than the canonical NS mass of 1.35 \Msun~ \citep{kiziltan13,smedley14}. The probability of any particular system having a NS companion, $P_{\rm NS}$, can be computed for a given set of parameters for the companion mass distribution:
\begin{equation}
P_{\rm NS} = \frac{\int_{M_{2,{\rm min}}}^{\infty} dM_2~ f_{\rm NS}~ p_{\rm NS}~ h(M_2, \mf, M_1)}{p(\mf \given \bs{\theta})}\label{eq:P_NS}
\end{equation}

Our companion mass model parameters are then $\bs{\theta} = (\mu_{\rm WD}, \sigma_{\rm WD}, f_{\rm NS})$. For $\mu_{\rm WD}$, we use a uniform prior from $0.2-1.4~\Msun$; we use a logarithmic prior for $\sigma_{\rm WD}$ over the range $0.02-2.0~\Msun$. Finally, we use a uniform prior over the dimensionless NS fraction, $f_{\rm NS}$, from $0-1$. The model parameters are summarized in Table~\ref{tbl:parameters}.

@@

	\startdata
		\multicolumn{2}{c}{\multirow{2}{*}{Priors}} & $\mathcal{U}(0.2, 1)$ & $\propto \sigma^{-1}$  & $\mathcal{U}(0, 1)$ \\
		\multicolumn{2}{c}{} & & $(0.02 < \sigma/\Msun < 2)$ & \\
		\cutinhead{Test Cases}
		\multirow{2}{*}{Test 1} & True & 0.7 & 0.2 & 0.0 \\
		 & MAP & 0.74 & 0.18 & 0.0 \\
		 \hline
		\multirow{2}{*}{Test 2} & True & 0.7 & 0.2 & 0.1 \\
		 & MAP & 0.74 & 0.2 & 0.11 \\
		 \hline
		\multirow{2}{*}{Test 3} & True & \nodata & \nodata & 0.1 \\
		 & MAP & 0.64 & 0.5 & 0.14 \\
		 \cutinhead{ELM Sample}
		 & MAP & 0.71 & 0.26 & 0.0
	\enddata

@@

\begin{figure*}[h!]
\begin{center}
\includegraphics[width=0.75\textwidth]{many-panel.pdf}
\caption{Results from the three tests described in Section~\ref{sec:tests}. The leftmost column shows histograms of $M_2$ drawn from each of our test distributions. Overplotted as solid lines are the MAP models. The second column shows samples from the posterior distributions of $\mu_{\rm WD}$ and $\sigma_{\rm WD}$. The dashed lines in the top two panels show the true values that the sample systems were drawn from. Contours designate the 68\% and 95\% contours. Since the third model was not drawn from a Gaussian distribution, there is no true parameter set. The third panel shows posterior samples for $f_{\rm NS}$ and $\sigma_{\rm WD}$; here again the dashed lines show the input values.  }
\label{fig:tests}
\end{center}
\end{figure*}

@@

\begin{figure*}[h!]
\begin{center}
\includegraphics[width=0.75\textwidth]{PNS.pdf}
\caption{ The individual LMWD systems (ordered by increasing $\mf$) and their corresponding $P_{\rm NS}$ for each of our three tests. Tick marks along the bottom show those systems that are true NSs.}
\label{fig:P_NS}
\end{center}
\end{figure*}

@@

The ELM WD sample is composed of 55 systems with radial velocity variations fit to orbital solutions, which provide precise measurements of $\period$ and $K$. Fitting the WDs' spectra to templates provides precisely determined $M_1$ values; we use the spectroscopic solutions of \citet{gianninas14}.

@@

\begin{figure*}[h!]
\begin{center}
\includegraphics[width=0.95\textwidth]{real-data.pdf}
\caption{Results from applying our model to the ELM WDs. The first panel shows the MAP $M_2$ distribution (solid black) and random samples from the posterior (grey lines). The second panel shows posterior samples of $\mu$ and $\sigma$; the MAP Gaussian model has $\mu_{\rm WD}= 0.71~\Msun$ and $\sigma_{\rm WD}= 0.26~\Msun$. The third panel shows posterior samples of $\mu$ and $f_{\rm NS}$. The last panel lists individual LMWDs in the ELM sample (ordered by increasing $\mf$) and shows each of their corresponding NS probabilities. The three systems with all $P_{\rm NS}$ values at 0\% are the three eclipsing systems with measured $M_2$.}
\label{fig:ELM_post}
\end{center}
\end{figure*}

@@

The results from applying our model to the ELM sample are shown in Figure \ref{fig:ELM_post}. The MAP model has parameters $\mu_{\rm WD} = 0.71~\Msun$, $\sigma_{\rm WD} = 0.26~\Msun$, and $f_{\rm NS} = 0\%$. The marginal posterior over $\mu_{\rm WD}$ and $\sigma_{\rm WD}$ has a tail toward larger $\sigma_{\rm WD}$, which could indicate that the true WD distribution may not be exactly Gaussian. It is interesting that the best fit Gaussian for the companions to the ELM WD sample is similar to that of the population of single DA WDs in SDSS, with a mean of 0.6 $\Msun$ \citep{kleinman13}. Our distribution is significantly wider ({\bf $\sigma \approx 0.26~\Msun$} compared with $\sigma \approx 0.1~\Msun$), possibly due to mass transfer affecting the mass distribution of the unseen primary WDs as well.

@@

The rightmost panel in Figure~\ref{fig:ELM_post} indicates there are two LMWDs with substantial $P_{\rm NS}$: SDSS J081133.6$+$022556.8 and SDSS J174140.5$+$652638.7. X-ray non-detections of SDSS J174140.5$+$652638.7 indicate its companion is unlikely to be a NS \citep{kilic14}. Searches for radio and X-ray emission from SDSS J081133.6$+$022556.8 are ongoing.

>>>>

\begin{abstract}
Measuring the masses of companions to single-line spectroscopic binary stars is (in general) not possible because of the unknown orbital plane inclination.  Even when the mass of the visible star can be measured, only a lower limit can be placed on the mass of the unseen companion. However, since these inclination angles should be isotropically distributed, for a large enough, unbiased sample, the  companion mass distribution can be deconvolved from the distribution of observables. In this work, we construct a hierarchical probabilistic model to infer properties of unseen companion stars given observations of the orbital period and projected radial velocity of the primary star. We then apply this model to {\bf three mock} samples of low mass white dwarfs (LMWDs, $M\lesssim0.45~\Msun$). We use a mixture of two Gaussians to model the WD and neutron star (NS) companion mass distributions. Our model successfully recovers the initial parameters of {\bf these} mock data sets. We then apply our model to 55 WDs in the extremely low mass (ELM) WD Survey. Our maximum a posteriori model for the WD companion population has a mean mass, $\mu_{\rm WD}$, of $0.71~\Msun$ with a standard deviation, $\sigma_{\rm WD}$, of $0.26~\Msun$; the fraction of NS companions, $f_{\rm NS}$, is consistent with zero. However, the marginal posterior distribution over the NS fraction has a significant tail up to $f_{\rm NS} \approx 16\%$. We make samples from the posterior distribution publicly available so that future observational efforts may compute the NS probability for newly discovered low mass WDs.
\end{abstract}

@@

Except in cases of extreme metallicity \citep{kilic07}, the Galaxy is not old enough to produce LMWDs ($M\lesssim0.45~ \Msun$) through single star evolution. These objects are formed through dynamical interactions with another star, and are therefore expected to be found in binary systems \citep{han98,nelemans00,nelemans01,vdSluys06,woods12}. In their seminal work, \citet{marsh95} discovered companions to five LMWDs, confirming these theoretical expectations, which has been followed by several other searches finding companions to LMWDs \citep{maxted00,nelemans05,rebassa11}. The ELM WD Survey \citep{ELMI} identifies LMWDs in the Sloan Digital Sky Survey \citep[SDSS;][]{york00} and elsewhere for spectroscopic follow-up, focusing on extremely low mass WDs ($M\lesssim0.3~ \Msun$). After these authors' initial investigation found that 11 of 12 LMWDs had close binary companions, further spectroscopic follow-up has now brought the sample of ELM WDs to 61 systems, 55 of which have measured radial velocity amplitudes and orbital periods \citep{ELMII, ELMIII, ELMIV, ELMV}. We refer to these 55 systems as the ELM sample.

While the orbital periods and radial velocities indicate the companions to these LMWDs are most likely WDs, due to the unmeasured inclination angle, LMWDs could host NS companions \citep{vLeeuwen07}. Indeed, LMWDs are observed as companions of millisecond pulsars \citep{vKerkwijk96,callanan98,bassa06,antoniadis12}. {\bf Finding even one additional system is extremely interesting since radial velocity measurements from optical spectra when combined with precise radio data give a NS mass measurement.} However, radio searches for pulsed emission and searches for X-ray emission from LMWD companions have been unsuccessful \citep{agueros09b,agueros09a,kilic13}.

@@

The ELM sample is now large enough that the NS fraction and WD companion mass distribution can be statistically constrained. {\bf Constraints on the WD companion mass distribution to LMWDs provide a clear observable for population synthesis studies to match.} In this work, we develop a probabilistic model to infer parameters of an assumed form for the mass distribution of companions to LMWDs. Our method is similar to that employed by \citet{ozel12} and \citet{kiziltan13} to describe the mass distribution of NSs in binaries using post-Keplerian parameters. We focus on several specific questions: 1.\ Can the population as a whole be modeled using a simple description of the companion masses? 2.\ How does the companion mass distribution compare to predictions from population synthesis simulations?  3.\ What is the rate of NS-LMWD binaries implied by our model? 4.\ What are the resulting distributions of NS probabilities for individual systems in the ELM sample?

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[angle=90,width=0.95\columnwidth]{f1.eps}
\caption{The $M_1$ - $\period$ distribution of the ELM WD sample (circles) and the known WD-NS binaries (triangles). The three eclipsing systems in the ELM sample with known $M_2$ are shown as filled circles, and the masses of the ELM WDs without detected radial velocity variations are shown by the arrows. From $M_1$ and $\period$ alone, the two populations are indistinguishable.}
\label{fig:Porb-M1}
\end{center}
\end{figure}

@@

We must now choose a functional form for the companion mass distribution,  $p(M_2\given \bs{\theta})$. For all experiments -- including that with the real data -- we use a two-component Gaussian mixture model to fit the data. We generate mock data with different mixture component forms. We truncate the distributions using physically motivated bounds so that the WD component is restricted to the range $M_2\in [0.2,\wdupper]~\Msun$ and the NS component is restricted to $M_2\in [1.3,2.0]~\Msun$. We then have:
\begin{align}
	p(M_2 \given \bs{\theta}) &= \left[ (1-f_{\rm NS})~p_{\rm WD} + f_{\rm NS}~p_{\rm NS} \right] 
\end{align}
where 
\begin{align}
	p_{\rm WD} &= \mathcal{N}(M_2 \given \mu_{\rm WD}, \sigma^2_{\rm WD}); ~0.2 < \frac{M_2}{\Msun} < \wdupper, \\
	p_{\rm NS} &= \mathcal{N}(M_2 \given \mu_{\rm NS}, \sigma^2_{\rm NS}); ~1.3 < \frac{M_2}{\Msun} < 2,
\end{align}
and $\mathcal{N}$ is the (truncated, but properly normalized) normal distribution with mean $\mu$ and variance $\sigma^2$, and the distributions are limited to the ranges specified. {\bf To reduce the number of parameters in our model} we fix $\mu_{\rm NS}$ and $\sigma_{\rm NS}$ to:
\begin{align}
	\mu_{\rm NS} &= 1.4~\Msun\\
	\sigma_{\rm NS} &= 0.05~\Msun
\end{align}
based on indications that NSs in certain binaries may be somewhat more massive than the canonical NS mass of 1.35 \Msun~ \citep{kiziltan13,smedley14}. The probability of any particular system having a NS companion, $P_{\rm NS}$, can be computed for a given set of parameters for the companion mass distribution:
\begin{equation}
P_{\rm NS} = \frac{\int_{M_{2,{\rm min}}}^{\infty} dM_2~ f_{\rm NS}~ p_{\rm NS}~ h(M_2, \mf, M_1)}{p(\mf \given \bs{\theta})}\label{eq:P_NS}
\end{equation}

Our companion mass model parameters are then $\bs{\theta} = (\mu_{\rm WD}, \sigma_{\rm WD}, f_{\rm NS})$. For $\mu_{\rm WD}$, we use a uniform prior from $0.2-1.0~\Msun$; we use a logarithmic ({\bf scale-invariant}) prior for $\sigma_{\rm WD}$ over the range $0.02-1.0~\Msun$. Finally, we use a uniform prior over the dimensionless NS fraction, $f_{\rm NS}$, from $0-1$. The model parameters are summarized in Table~\ref{tbl:parameters}.

@@

	\startdata
		\multicolumn{2}{c}{\multirow{2}{*}{Priors}} & $\mathcal{U}(0.2, 1)$ & $\propto \sigma^{-1}$  & $\mathcal{U}(0, 1)$ \\
		\multicolumn{2}{c}{} & & $(0.02 < \sigma/\Msun < 2.0)$ & \\
		\cutinhead{Test Cases}
		\multirow{2}{*}{Test 1} & True & 0.7 & 0.2 & 0.0 \\
		 & MAP & 0.74 & 0.18 & 0.0 \\
		 \hline
		\multirow{2}{*}{Test 2} & True & 0.7 & 0.2 & 0.1 \\
		 & MAP & 0.74 & 0.2 & 0.11 \\
		 \hline
		\multirow{2}{*}{Test 3} & True & \nodata & \nodata & 0.1 \\
		 & MAP & 0.64 & 0.5 & 0.14 \\
		 \cutinhead{ELM Sample}
		 & MAP & 0.71 & 0.26 & 0.0
	\enddata

@@

\begin{figure*}[h!]
\begin{center}
\includegraphics[width=0.75\textwidth]{f2.pdf}
\caption{Results from the three tests described in Section~\ref{sec:tests}. The leftmost column shows histograms of $M_2$ drawn from each of our test distributions. Overplotted as solid lines are the MAP models. The second column shows samples from the posterior distributions of $\mu_{\rm WD}$ and $\sigma_{\rm WD}$. The dashed lines in the top two panels show the true values that the sample systems were drawn from. Contours designate the 68\% and 95\% contours. Since the third model was not drawn from a Gaussian distribution, there is no true parameter set. The third panel shows posterior samples for $f_{\rm NS}$ and $\sigma_{\rm WD}$; here again the dashed lines show the input values.  }
\label{fig:tests}
\end{center}
\end{figure*}

@@

\begin{figure*}[h!]
\begin{center}
\includegraphics[width=0.75\textwidth]{f3.pdf}
\caption{ The individual LMWD systems (ordered by increasing $\mf$) and their corresponding $P_{\rm NS}$ for each of our three tests. Tick marks along the bottom show those systems that are true NSs.}
\label{fig:P_NS}
\end{center}
\end{figure*}

@@

The ELM WD sample is composed of 55 systems with radial velocity variations fit to orbital solutions, which provide precise measurements of $\period$ and $K$. Fitting the WDs' spectra to templates provides precisely determined $M_1$ values; we use the spectroscopic solutions of \citet{gianninas14}. {\bf These mass measurements are precisely determined, however the spectroscopic mass measurements may be affected by contamination from the less luminous companion or the ``high log $g$ problem'' due to inaccuracies in the 1-D WD atmospheric models \citep{tremblay13}. These limitations should only affect the coolest WDs in the ELM sample, therefore we suggest this effect is minor.}

@@

\begin{figure*}[h!]
\begin{center}
\includegraphics[width=0.95\textwidth]{f4.pdf}
\caption{Results from applying our model to the ELM WDs. The first panel shows the MAP $M_2$ distribution (solid black) and random samples from the posterior (grey lines). The second panel shows posterior samples of $\mu$ and $\sigma$; the MAP Gaussian model has $\mu_{\rm WD}= 0.71~\Msun$ and $\sigma_{\rm WD}= 0.26~\Msun$. The third panel shows posterior samples of $\mu$ and $f_{\rm NS}$. The last panel lists individual LMWDs in the ELM sample (ordered by increasing $\mf$) and shows each of their corresponding NS probabilities. The three systems with all $P_{\rm NS}$ values at 0\% are the three eclipsing systems with measured $M_2$.}
\label{fig:ELM_post}
\end{center}
\end{figure*}

@@

The results from applying our model to the ELM sample are shown in Figure \ref{fig:ELM_post}. The MAP model has parameters $\mu_{\rm WD} = 0.71~\Msun$, $\sigma_{\rm WD} = 0.26~\Msun$, and $f_{\rm NS} = 0\%$. The marginal posterior over $\mu_{\rm WD}$ and $\sigma_{\rm WD}$ has a tail toward larger $\sigma_{\rm WD}$, which could indicate that the true WD distribution may not be exactly Gaussian. It is interesting that the best fit Gaussian for the companions to the ELM WD sample is similar to that of the population of single DA WDs in SDSS, with a mean of 0.6 $\Msun$ \citep{kleinman13}. Our distribution is significantly wider ({\bf $\sigma \approx 0.26~\Msun$} compared with $\sigma \approx 0.1~\Msun$), possibly due to {\bf past mass transfer phases increasing the masses of the unseen primary WDs.} {\bf Several of these systems will merge within a Hubble time \citep{ELMV}, however their sub-Chandrasekhar combined mass would suggest that they are more likely to be underluminous, .Ia supernova progenitors rather than type Ia supernova progenitors. }

@@

The rightmost panel in Figure~\ref{fig:ELM_post} indicates there are two LMWDs with substantial $P_{\rm NS}$: SDSS J081133.6$+$022556.8 and SDSS J174140.5$+$652638.7. X-ray non-detections of SDSS J174140.5$+$652638.7 indicate its companion is unlikely to be a NS \citep{kilic14}. Searches for radio and X-ray emission from SDSS J081133.6$+$022556.8 are ongoing. {\bf Figure~\ref{fig:ELM_post} shows a general trend that systems with higher $\mf$'s have higher $P_{\rm NS}$ values. This is due to the effect of $M_2$ on $\mf$ in Equation~\ref{eq:massfunc}. Systems with higher $\mf$'s are therefore ideal targets to search for NS companions to LMWDs.}
